Debugging of RxJS-based Applications

### 2020-08-21 paper.tex
Future Work

TODO

A future paper will elaborate on the selection of a RP debugging tool (e.g., a full reactive debugger or a visualizer using marble diagrams), how and where (i.e. which IDE or browser) it should be integrated in a future paper.

>>>>

The answer on which RP debugging tool exactly (e.g., a full reactive debugger or a visualizer using marble diagrams) we are going to integrate, how such an integration will look like in detail, as well as the answer on RQ3 will be part of our future work on the topic of ``Debugging RxJS-based Applications''.
